### 2014-10-30 thesis/appendix/tr-oner-threshold-features.tex
Complete all results tables for the trauma data set

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{1R Accuracy - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
66.905 & 59 & 75.64\% & iss, upperlimbonly, triss, arrivalmode, mechcode, ext3, chestany, headface, faceany, neckany, any\_stroketia, headany, bodyregions, externalany, lowerlimbany, spineany, upperlimbany, abdoany, traumateam, penetrating, face3, normalvitals, bp, sex, pr, rr, gcs, traumatier, transfer, icu, head3, chest3, neck3, headminor, operation, alcohol, mentalhealth, upperlimboponly, lowerlimbnopelvis, english, any\_heart, any\_cancer, any\_kidney, any\_liver, charlson, married, any\_dm, laparotomy, upper3, spine3, abdo3, lower3, thoracotomy, lower\_limbop, neurosurgery, upper\_limbop, pelvic\_fracture, anypelvis, age \\ \hline
67.905 & 4 & 5.13\% & iss, upperlimbonly, triss, arrivalmode \\ \hline
68.905 & 2 & 2.56\% & iss, upperlimbonly \\ \hline
69.905 & 2 & 2.56\% & iss, upperlimbonly \\ \hline
71.905 & 0 & 0.00\% &  \\ \hline
74.405 & 0 & 0.00\% &  \\ \hline
76.905 & 0 & 0.00\% &  \\ \hline
81.905 & 0 & 0.00\% &  \\ \hline
86.905 & 0 & 0.00\% &  \\ \hline
96.905 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\vspace{1cm}
\vfill
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{1R Accuracy - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
66.905 & 55 & 70.51\% & triss, iss, upperlimbonly, arrivalmode, mechcode, bodyregions, ext3, chestany, spineany, abdoany, head3, upperlimbany, lowerlimbany, headface, externalany, neckany, any\_stroketia, faceany, headany, gcs, normalvitals, sex, icu, transfer, traumatier, neck3, penetrating, traumateam, face3, chest3, any\_dm, headminor, operation, alcohol, mentalhealth, upperlimboponly, lowerlimbnopelvis, english, any\_heart, any\_cancer, any\_kidney, any\_liver, abdo3, charlson, married, thoracotomy, lower3, upper3, spine3, lower\_limbop, laparotomy, neurosurgery, anypelvis, upper\_limbop, pelvic\_fracture \\ \hline
67.905 & 4 & 5.13\% & triss, iss, upperlimbonly, arrivalmode \\ \hline
68.905 & 3 & 3.85\% & triss, iss, upperlimbonly \\ \hline
69.905 & 3 & 3.85\% & triss, iss, upperlimbonly \\ \hline
71.905 & 1 & 1.28\% & triss \\ \hline
74.405 & 0 & 0.00\% &  \\ \hline
76.905 & 0 & 0.00\% &  \\ \hline
81.905 & 0 & 0.00\% &  \\ \hline
86.905 & 0 & 0.00\% &  \\ \hline
96.905 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected from the trauma data set using varying accuracy thresholds for the 1R feature selector. Features are shown in ranked order, from highest to lowest accuracy.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{1R Accuracy - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
66.905 & 59 & 75.64\% & iss, upperlimbonly, triss, arrivalmode, mechcode, ext3, chestany, headface, faceany, neckany, any\_stroketia, headany, bodyregions, externalany, lowerlimbany, spineany, upperlimbany, abdoany, traumateam, penetrating, face3, normalvitals, bp, sex, pr, rr, gcs, traumatier, transfer, icu, head3, chest3, neck3, headminor, operation, alcohol, mentalhealth, upperlimboponly, lowerlimbnopelvis, english, any\_heart, any\_cancer, any\_kidney, any\_liver, charlson, married, any\_dm, laparotomy, upper3, spine3, abdo3, lower3, thoracotomy, lower\_limbop, neurosurgery, upper\_limbop, pelvic\_fracture, anypelvis, age \\ \hline
67.905 & 4 & 5.13\% & iss, upperlimbonly, triss, arrivalmode \\ \hline
68.905 & 2 & 2.56\% & iss, upperlimbonly \\ \hline
69.905 & 2 & 2.56\% & iss, upperlimbonly \\ \hline
71.905 & 0 & 0.00\% & - \\ \hline
74.405 & 0 & 0.00\% & - \\ \hline
76.905 & 0 & 0.00\% & - \\ \hline
81.905 & 0 & 0.00\% & - \\ \hline
86.905 & 0 & 0.00\% & - \\ \hline
96.905 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\vspace{1cm}
\vfill
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{1R Accuracy - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
66.905 & 55 & 70.51\% & triss, iss, upperlimbonly, arrivalmode, mechcode, bodyregions, ext3, chestany, spineany, abdoany, head3, upperlimbany, lowerlimbany, headface, externalany, neckany, any\_stroketia, faceany, headany, gcs, normalvitals, sex, icu, transfer, traumatier, neck3, penetrating, traumateam, face3, chest3, any\_dm, headminor, operation, alcohol, mentalhealth, upperlimboponly, lowerlimbnopelvis, english, any\_heart, any\_cancer, any\_kidney, any\_liver, abdo3, charlson, married, thoracotomy, lower3, upper3, spine3, lower\_limbop, laparotomy, neurosurgery, anypelvis, upper\_limbop, pelvic\_fracture \\ \hline
67.905 & 4 & 5.13\% & triss, iss, upperlimbonly, arrivalmode \\ \hline
68.905 & 3 & 3.85\% & triss, iss, upperlimbonly \\ \hline
69.905 & 3 & 3.85\% & triss, iss, upperlimbonly \\ \hline
71.905 & 1 & 1.28\% & triss \\ \hline
74.405 & 0 & 0.00\% & - \\ \hline
76.905 & 0 & 0.00\% & - \\ \hline
81.905 & 0 & 0.00\% & - \\ \hline
86.905 & 0 & 0.00\% & - \\ \hline
96.905 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

### 2014-10-30 thesis/appendix/tr-rankeddist-summary.tex
Complete all results tables for the trauma data set

\vspace{15cm}
\caption{}

@@

\begin{tabular}{|*{21}{l|}}

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} \\ \hline
1 & 68.16\% & 0.27\% & 70.59\% & 0.30\% & 72.28\% & 0.30\% & 75.05\% & 0.29\% & 74.28\% & 0.25\% & 76.14\% & 0.24\% & 74.50\% & 0.23\% & 76.27\% & 0.19\% & 74.75\% & 0.30\% & 77.04\% & 0.22\% \\ \hline
5 & 68.43\% & 0.21\% & 70.35\% & 0.16\% & 73.40\% & 0.28\% & 75.19\% & 0.27\% & 74.76\% & 0.22\% & 76.31\% & 0.07\% & 75.01\% & 0.27\% & 76.37\% & 0.26\% & 75.41\% & 0.18\% & 76.88\% & 0.16\% \\ \hline
10 & 69.84\% & 0.12\% & 70.50\% & 0.12\% & 73.98\% & 0.19\% & 74.93\% & 0.18\% & 75.22\% & 0.21\% & 76.17\% & 0.12\% & 75.59\% & 0.25\% & 76.29\% & 0.16\% & 75.57\% & 0.14\% & 76.62\% & 0.24\% \\ \hline
15 & 70.14\% & 0.25\% & 70.42\% & 0.22\% & 74.58\% & 0.25\% & 74.96\% & 0.21\% & 75.49\% & 0.18\% & 76.14\% & 0.20\% & 75.83\% & 0.21\% & 76.20\% & 0.17\% & 76.46\% & 0.19\% & 76.81\% & 0.19\% \\ \hline

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} \\ \hline
1 & 0.668 & 0.0029 & 0.685 & 0.0039 & 0.773 & 0.0027 & 0.802 & 0.0029 & 0.796 & 0.0014 & 0.827 & 0.0014 & 0.801 & 0.0016 & 0.829 & 0.0014 & 0.806 & 0.0018 & 0.832 & 0.0009 \\ \hline
5 & 0.665 & 0.0030 & 0.681 & 0.0027 & 0.781 & 0.0026 & 0.804 & 0.0020 & 0.805 & 0.0018 & 0.830 & 0.0009 & 0.812 & 0.0014 & 0.832 & 0.0012 & 0.815 & 0.0008 & 0.834 & 0.0008 \\ \hline
10 & 0.677 & 0.0041 & 0.684 & 0.0031 & 0.785 & 0.0021 & 0.806 & 0.0018 & 0.808 & 0.0009 & 0.827 & 0.0015 & 0.818 & 0.0015 & 0.834 & 0.0013 & 0.818 & 0.0009 & 0.835 & 0.0011 \\ \hline
15 & 0.682 & 0.0044 & 0.680 & 0.0029 & 0.792 & 0.0021 & 0.806 & 0.0016 & 0.817 & 0.0016 & 0.828 & 0.0009 & 0.822 & 0.0017 & 0.832 & 0.0010 & 0.826 & 0.0012 & 0.836 & 0.0009 \\ \hline

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - No Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} \\ \hline
1 & 67.03\% & 0.19\% & 69.75\% & 0.18\% & 71.88\% & 0.21\% & 74.17\% & 0.17\% & 73.58\% & 0.28\% & 75.15\% & 0.17\% & 73.42\% & 0.28\% & 74.25\% & 0.20\% & 74.41\% & 0.31\% & 74.72\% & 0.31\% \\ \hline
5 & 67.61\% & 0.24\% & 69.93\% & 0.21\% & 72.57\% & 0.39\% & 74.17\% & 0.31\% & 73.57\% & 0.21\% & 75.02\% & 0.20\% & 73.10\% & 0.19\% & 74.13\% & 0.12\% & 74.02\% & 0.23\% & 75.05\% & 0.26\% \\ \hline
10 & 68.26\% & 0.14\% & 70.06\% & 0.18\% & 72.77\% & 0.32\% & 74.01\% & 0.22\% & 74.27\% & 0.26\% & 74.90\% & 0.23\% & 73.87\% & 0.16\% & 74.46\% & 0.20\% & 73.88\% & 0.27\% & 74.87\% & 0.24\% \\ \hline
15 & 69.23\% & 0.29\% & 70.39\% & 0.32\% & 73.14\% & 0.18\% & 73.93\% & 0.18\% & 74.49\% & 0.21\% & 75.20\% & 0.24\% & 74.33\% & 0.24\% & 74.60\% & 0.20\% & 74.19\% & 0.20\% & 74.82\% & 0.19\% \\ \hline

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - No Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} \\ \hline
1 & 0.653 & 0.0030 & 0.676 & 0.0032 & 0.771 & 0.0023 & 0.798 & 0.0022 & 0.794 & 0.0020 & 0.816 & 0.0014 & 0.802 & 0.0020 & 0.818 & 0.0009 & 0.807 & 0.0013 & 0.822 & 0.0017 \\ \hline
5 & 0.660 & 0.0040 & 0.679 & 0.0048 & 0.777 & 0.0026 & 0.797 & 0.0021 & 0.802 & 0.0013 & 0.817 & 0.0015 & 0.805 & 0.0014 & 0.820 & 0.0017 & 0.807 & 0.0017 & 0.824 & 0.0014 \\ \hline
10 & 0.661 & 0.0027 & 0.680 & 0.0041 & 0.780 & 0.0024 & 0.799 & 0.0013 & 0.806 & 0.0021 & 0.819 & 0.0010 & 0.810 & 0.0013 & 0.823 & 0.0011 & 0.810 & 0.0014 & 0.824 & 0.0012 \\ \hline
15 & 0.674 & 0.0038 & 0.682 & 0.0058 & 0.786 & 0.0012 & 0.799 & 0.0010 & 0.810 & 0.0010 & 0.821 & 0.0019 & 0.814 & 0.0014 & 0.824 & 0.0016 & 0.815 & 0.0013 & 0.825 & 0.0014 \\ \hline

>>>>

\vspace{15.7cm}
\caption{Results for the $k$-NN classifier with our proposed Ranked Distance approach on the trauma data set with and without discretisation, for varying numbers of numbers $k$ and decay constant $c$.}

@@

\begin{tabular}{|l|*{10}{cc|}}

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- \\ \hline
  1 & 68.16\% & 0.27\% & 70.59\% & 0.30\% & 72.28\% & 0.30\% & 75.05\% & 0.29\% & 74.28\% & 0.25\% & 76.14\% & 0.24\% & 74.50\% & 0.23\% & 76.27\% & 0.19\% & 74.75\% & 0.30\% & 77.04\% & 0.22\% \\
  5 & 68.43\% & 0.21\% & 70.35\% & 0.16\% & 73.40\% & 0.28\% & 75.19\% & 0.27\% & 74.76\% & 0.22\% & 76.31\% & 0.07\% & 75.01\% & 0.27\% & 76.37\% & 0.26\% & 75.41\% & 0.18\% & 76.88\% & 0.16\% \\
  10 & 69.84\% & 0.12\% & 70.50\% & 0.12\% & 73.98\% & 0.19\% & 74.93\% & 0.18\% & 75.22\% & 0.21\% & 76.17\% & 0.12\% & 75.59\% & 0.25\% & 76.29\% & 0.16\% & 75.57\% & 0.14\% & 76.62\% & 0.24\% \\
  15 & 70.14\% & 0.25\% & 70.42\% & 0.22\% & 74.58\% & 0.25\% & 74.96\% & 0.21\% & 75.49\% & 0.18\% & 76.14\% & 0.20\% & 75.83\% & 0.21\% & 76.20\% & 0.17\% & 76.46\% & 0.19\% & 76.81\% & 0.19\% \\

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- \\ \hline
  1 & 0.668 & 0.0029 & 0.685 & 0.0039 & 0.773 & 0.0027 & 0.802 & 0.0029 & 0.796 & 0.0014 & 0.827 & 0.0014 & 0.801 & 0.0016 & 0.829 & 0.0014 & 0.806 & 0.0018 & 0.832 & 0.0009 \\
  5 & 0.665 & 0.0030 & 0.681 & 0.0027 & 0.781 & 0.0026 & 0.804 & 0.0020 & 0.805 & 0.0018 & 0.830 & 0.0009 & 0.812 & 0.0014 & 0.832 & 0.0012 & 0.815 & 0.0008 & 0.834 & 0.0008 \\
  10 & 0.677 & 0.0041 & 0.684 & 0.0031 & 0.785 & 0.0021 & 0.806 & 0.0018 & 0.808 & 0.0009 & 0.827 & 0.0015 & 0.818 & 0.0015 & 0.834 & 0.0013 & 0.818 & 0.0009 & 0.835 & 0.0011 \\
  15 & 0.682 & 0.0044 & 0.680 & 0.0029 & 0.792 & 0.0021 & 0.806 & 0.0016 & 0.817 & 0.0016 & 0.828 & 0.0009 & 0.822 & 0.0017 & 0.832 & 0.0010 & 0.826 & 0.0012 & 0.836 & 0.0009 \\

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - No Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- \\ \hline
  1 & 67.03\% & 0.19\% & 69.75\% & 0.18\% & 71.88\% & 0.21\% & 74.17\% & 0.17\% & 73.58\% & 0.28\% & 75.15\% & 0.17\% & 73.42\% & 0.28\% & 74.25\% & 0.20\% & 74.41\% & 0.31\% & 74.72\% & 0.31\% \\
  5 & 67.61\% & 0.24\% & 69.93\% & 0.21\% & 72.57\% & 0.39\% & 74.17\% & 0.31\% & 73.57\% & 0.21\% & 75.02\% & 0.20\% & 73.10\% & 0.19\% & 74.13\% & 0.12\% & 74.02\% & 0.23\% & 75.05\% & 0.26\% \\
  10 & 68.26\% & 0.14\% & 70.06\% & 0.18\% & 72.77\% & 0.32\% & 74.01\% & 0.22\% & 74.27\% & 0.26\% & 74.90\% & 0.23\% & 73.87\% & 0.16\% & 74.46\% & 0.20\% & 73.88\% & 0.27\% & 74.87\% & 0.24\% \\
  15 & 69.23\% & 0.29\% & 70.39\% & 0.32\% & 73.14\% & 0.18\% & 73.93\% & 0.18\% & 74.49\% & 0.21\% & 75.20\% & 0.24\% & 74.33\% & 0.24\% & 74.60\% & 0.20\% & 74.19\% & 0.20\% & 74.82\% & 0.19\% \\

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - No Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- \\ \hline
  1 & 0.653 & 0.0030 & 0.676 & 0.0032 & 0.771 & 0.0023 & 0.798 & 0.0022 & 0.794 & 0.0020 & 0.816 & 0.0014 & 0.802 & 0.0020 & 0.818 & 0.0009 & 0.807 & 0.0013 & 0.822 & 0.0017 \\
  5 & 0.660 & 0.0040 & 0.679 & 0.0048 & 0.777 & 0.0026 & 0.797 & 0.0021 & 0.802 & 0.0013 & 0.817 & 0.0015 & 0.805 & 0.0014 & 0.820 & 0.0017 & 0.807 & 0.0017 & 0.824 & 0.0014 \\
  10 & 0.661 & 0.0027 & 0.680 & 0.0041 & 0.780 & 0.0024 & 0.799 & 0.0013 & 0.806 & 0.0021 & 0.819 & 0.0010 & 0.810 & 0.0013 & 0.823 & 0.0011 & 0.810 & 0.0014 & 0.824 & 0.0012 \\
  15 & 0.674 & 0.0038 & 0.682 & 0.0058 & 0.786 & 0.0012 & 0.799 & 0.0010 & 0.810 & 0.0010 & 0.821 & 0.0019 & 0.814 & 0.0014 & 0.824 & 0.0016 & 0.815 & 0.0013 & 0.825 & 0.0014 \\
